Structured Versus Decorated Cospans

### 2022-03-16 ResponseToReviews.tex

{\kenny The boldface looks good to me, but I also like Christina's suggestions above if we really want to make an effort to appease this referee. I'm fine either way on this.}

{\john See if you like my new remarks in boldface, and give me a check mark if you do!  Kenny had checked this one off already, but I've changed it a lot.}

\item Given that Petri nets with structured cospans works, and Reaction Networks work, but open dynamical systems do not, I would like some more 
explanation of the differences here. The examples of graph, labeled 
graph, Petri net, reaction net are all examples of attributed C-Sets [1], the structured cospan construction in provided for arbitrary attributed 
C-Sets in Catlab.CategoricalAlgebra [2]. The open dynamical systems are not attributed C-Sets.(...)The examples in section 6 would be much stronger 
if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
conditions of theorem 4.1 or a counter example (...) Hopefully it is easy to check and provide some 
commentary 
on it in this paper.

{\bf Unfortunately not all cases of C-sets meet the conditions of Theorem 4.1.   For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of vertices.  So, this gives a structured cospan category to which Theorem 4.1 does not apply.   Finding extra conditions such that it \emph{does} apply is an interesting question, but it would take more thought.}

@@

{\john Actually it's really easy to prove that presheaf categories obey the conditions of Theorem 4.1:
given any functor $f : \mathsf{C} \to \mathsf{D}$ the left adjoint functor between presheaf categories $f_! : \widehat{\mathsf{C}} \to \widehat{\mathsf{D}}$ obeys the conditions of Theorems 4.1 and 4.2.   So I think we can easily add this as a corollary, maybe right after Theorem 4.2, to get a pile of examples.   Obvious to us, but not to everyone.  Should I do it?}

{\chris Sounds like a great idea to me!! I was also a bit scared to go into this when I first saw it, but I kinda thought morally we should, and now 
it looks like it won't be a disaster, and in fact a very fruitful result!! So yes please, do it and let me know what I can do to help except 
proofread it.}

{\chris Also perhaps we should add those references they provide somewhere.}

{\john Now I think this is a bit harder than I thought.  I started writing stuff:

\vskip 1em
\begin{quote}
Presheaf categories provide many examples of  Theorem 4.1.  Suppose $f \colon C \to D$ is any functor between small categories.  Then precomposition with $f$ gives a functor $f^\ast \colon \widehat{D} \to \widehat{C}$ between their presheaf categories, and this has a left adjoint $f_! \colon \widehat{C} \to \widehat{D}$.   
\end{quote}

This is a good enough situation to build a structured cospan category, but the right adjoint $f^\ast$ may not be an opfibration, in which case we can't apply Theorem 4.1 --- right?

With a lot of help from Todd Trimble's I once figured out when $f^\ast$ \emph{is} an opfibration, but remembering that argument and writing this up would take some work.  And I don't really feel like expanding the paper in such a way --- we've got more than enough already.   So how about if just tell the referee this is a great idea but it would take more thought?   See if you like my boldface comment above.  
}

### 2022-03-16 cospans_new.tex
I dealt with comment 10 - maybe.

The hypothesis of this theorem is essentially a way of asking that the fibers of the induced opfibration $U \maps \inta F \to \A$ have finite colimits which are preserved by the reindexing functors, and that the induced fiberwise monoidal structure is cocartesian.   Expanding on this a bit:
the fibers of $U$ are the same as the categories $F(a)$ for all $a \in \A$.   The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on each category $F(a)$ given by \cref{eq:explicitstructure1}.  The hypothesis of the theorem asks that the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$.  This implies
that the symmetric monoidal structure on $F(a)$ is cocartesian.

@@

>>>>

The hypothesis of this theorem is essentially a way of asking that the fibers of the induced opfibration $U \maps \inta F \to \A$ have finite colimits which are preserved by the reindexing functors, and that the induced fiberwise monoidal structure is cocartesian.   Expanding on this a bit:
the fibers of $U$ are the same as the categories $F(a)$ for all $a \in \A$.   The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on each category $F(a)$, as in \cref{eq:explicitstructure1}.  The hypothesis of the theorem asks that the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$.  This implies
that the symmetric monoidal structure on each category $F(a)$ is cocartesian.

@@

\iffalse
Presheaf categories provide many examples of \cref{thm:equiv}.  Suppose $\phi \maps \C \to \D$ is any functor between small categories.  Then precomposition with $\phi$ gives a functor $\phi^\ast \maps \widehat{\D} \to \widehat{\C}$ between their presheaf categories, and this has a left adjoint $\phi_! \maps \widehat{\C} \to \widehat{\D}$.   
\fi
